### 2016-09-06 notions.tex
starting to typeset ss proof for domain-separated PRF construction
no message

First, a set~$S$ is chosen according to some
distribution~$\distr{}{}$ over the collection of multisets
$\mathcal{S}$ associated with~$\Pi$, and then
$\Rep(S)$ is run to generate $(\pubaux,\privaux)$. \jnote{I thought we were going to let
the adversary choose~$S$?}
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
Adversary~$A$ is given~$\pubaux$~as input; it is also
provided with access to an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
returns $\Qry(\pubaux,\privaux,q)$ and increments
a counter if this result is in error.  The adversary wins if it
manages to cause at least~$r>0$ such errors among its queries.

@@

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
$S \getsr \distr{}{}$\\
$\mathrm{err}\gets 0$\\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(\pubaux,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$(a,\mathrm{err})$
}
}
\caption{Correctness of~$\Pi$ against (adaptive) adversary~$A$, when
  the represented multiset~$S$ is sampled according to distribution~$\distr{}{}$.}
\label{fig:correctness}
\end{figure}

In this experiment we track the time-complexity (relative to some
implied model of computation) and query-complexity (i.e., number of
queries) of the adversary~$A$.
We define the advantage of adversary~$A$ in the correctness experiment as
$\AdvCorrect{\Pi,\distr{}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{}{}, r,}{A}=1}$.
Overloading notation, we write $\AdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over all~$t$-time adversaries that ask at most~$q$ queries. Roughly, we say that a
set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon'$.
\jnote{Note~$q$ is overloaded here.}
%\jnote{Note that test includes err because we don't want to penalize
%the adversary's resources for computing $q(S)$.}

\heading{Comparison to Naor-Yogev definition.}
The style of the Naor-Yogev (NY) definition is slightly different. \jnote{Even if we ignore
all the other issues, chief among them the inconsistent way it treats the hash functions.}
Lifting their definition to our setting, the experiment is similar but the attacker
succeeds only if it outputs a single query $q$ for which
$\Qry(\pubaux,\privaux, q) \neq q(S)$  \emph{subject to the restriction that it did not
query $q$ to its $\TestOracle$ oracle}.
It will be interesting to understand formally the relation between our
definition and theirs.
Here are some observations:
\begin{enumerate}
\item Say a scheme is $\epsilon_{NY}$-secure under the NY definition.
Then we claim it is $(t,q, r, q\epsilon_{NY}/r)$-correct. To see
this, assume not. Then there is a $t$-time attacker~$A$ that, with
probability at least $\epsilon'=q\epsilon_{NY}/r$,
issues~$q$ Test-queries of which at least~$r$ cause errors. If we simply run~$A$ and then choose a random Test-query to
output, we succeed with probability at least $\epsilon' \cdot r/q$. It is unclear whether this is tight.

>>>>

First, a set~$S$ is chosen according to some
distribution~$\distr{}{}$ over the collection of multisets
$\mathcal{S}$ associated with~$\Pi$, and then
$\Rep(S)$ is run to generate $(\pubaux,\privaux)$. \jnote{I thought we were going to let
the adversary choose~$S$?}
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
Adversary~$A$ is given~$\pubaux$~as input; it is also
provided with access to an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
returns $\Qry(\pubaux,\privaux,q)$ and increments
a counter if this result is in error.  The adversary wins if it
manages to cause at least~$r>0$ such errors among its queries.
\jnote{If we are specializing the set-multiplicity data structures then we
may as well have the attacker query $x$ which gets translated to query $q_x$. If
we are trying to be more general then we should be consistent.} \jnote{Why does $A$ output
anything at all?}

@@

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
$S \getsr \distr{}{}$\\
$\mathrm{err}\gets 0$\\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(\pubaux,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$(a,\mathrm{err})$
}
}
\caption{Correctness of~$\Pi$ against an (adaptive) adversary~$A$, when
  the represented multiset~$S$ is sampled according to distribution~$\distr{}{}$.}
\label{fig:correctness}
\end{figure}

In this experiment we track the time complexity (relative to some
model of computation) and query complexity (i.e., number of
queries to $\TestOracle$) of~$A$.
We define the advantage of adversary~$A$ in the correctness experiment as
$\AdvCorrect{\Pi,\distr{}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{}{}, r,}{A}=1}$.
Overloading notation, we write $\AdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over
all~$t$-time adversaries that ask at most~$q$ queries. We say that a
set-representation data structure~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon'$.
\jnote{Note~$q$ is overloaded here.}
%\jnote{Note that test includes err because we don't want to penalize
%the adversary's resources for computing $q(S)$.}

\heading{Comparison to Naor-Yogev definition.}
The style of the Naor-Yogev definition is different from ours.
Lifting their definition\footnote{They focus specifically on set-representation data structures
with no false negatives, and consider worst-case choice of~$S$. Their data-structure syntax
also does not distinguish public and private portions of the representation. Nevertheless, it is straightforward
to extend their definition to more closely match ours.}
to our setting,
the experiment is similar but the attacker
succeeds only if it outputs a (single) query $q$ for which
$\Qry(\pubaux,\privaux, q) \neq q(S)$  \emph{subject to the restriction that it did not
previously query $q$ to its $\TestOracle$ oracle} (see Figure~\ref{fig:NYcorrectness}).

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
$S \getsr \distr{}{}$\\
$\mathcal{Q} \gets \emptyset$\\
%$\mathrm{err}\gets 0$\\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
$q \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\left(q \not \in \mathcal{Q}\right.$ and \\
\nudge $\left.\Qry(\pubaux,\privaux,q) \neq q(S)\right)$ \\
\nudge \nudge then Return 1\\
Return 0
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(\pubaux,\privaux,q)$\\
$\mathcal{Q} \gets \mathcal{Q} \cup \{q\}$ \\
%\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$(a,q(S))$
}
}
\caption{The Naor-Yogev definition of
correctness, adapted to our setting.}
\label{fig:NYcorrectness}
\end{figure}

It will be interesting to understand formally the relation between our
definition and theirs.
Here are some observations:
\begin{enumerate}
\item Say a scheme is $\epsilon_{NY}$-secure under the NY definition.
Then we claim it is $(t,q, r, q\epsilon_{NY}/r)$-correct. To see
this, assume not. Then there is a $t$-time attacker~$A$ that, with
probability at least $\epsilon'=q\epsilon_{NY}/r$,
issues~$q$ Test-queries of which at least~$r$ cause errors. If we simply run~$A$ and then choose a random Test-query to
output, we succeed with probability at least $\epsilon' \cdot r/q$. It is unclear whether this is tight.
